Title here

### 2017-05-16 portfolio/text/ms.Rmd
PWS seine sentence

Our findings across fishing strategies are in line with previous research at the
community and vessel levels [@kasperski2013; @sethi2012b; @sethi2014; @cline2017], but our
findings within strategies, with respect to individual year-to-year behavior,
provide new insights. Here, specializing tended to be associated with increased
revenue. This could be for a number of reasons. First, specialization can
increase fishing efficiency [@smith1986]. 
Similar efficiency gains from specialization are well known in 
agricultural fields [@ikerd1990; @abdulai2000].
Second, given the
availability of valuable resources, specializing can be highly profitable. For
instance, when cocoa prices have been high, Nigerian farmers have tended to
specialize on the crop [@mustapha1999] and specializing on valuable tobacco
farming can be the optimal strategy regardless of alternative crops
[@chavez2014]. In our analyses, fishers with the opportunity to fish highly
valuable sockeye salmon benefited the most from specializing. However,
specializing can have longterm risks if market, management, biological, or
environmental conditions change. For example, U.S. farmers specialized on wheat,
corn, or soybeans were hit harder than diversified farmers in the early 1980s
when a financial crisis hit [@ikerd1990].
Third, diversifying---a lack of
specialization---can happen as a consequence of non-ideal circumstances such
as poor availability of a more valuable resource. For example, Ugandan
households relying on forestry resources for income increase their income
portfolio diversity following downward economic shocks [@debela2012].
Because specialization inherently holds risk from ``putting all one's eggs in one
basket,'' it is not suprising that a decline in the most valuable resource
would lead to a shift towards diversification.
<!-- Response to A1 -->
Conversely, a specialization may appear as a response to increased revenue. A fisher who achieves high revenue from a hotspot of a particular fish species one year may choose to stop or pause fishing thereby indirectly limiting catch diversity. For example, pink and chum salmon are the dominant species caught in purse seine fisheries in Prince william Sound and their run timing rarely overlaps. If a fisher achieves high revenue with one species that fisher may cut the season short.

>>>>

Our findings across fishing strategies are in line with previous research at the
community and vessel levels [@kasperski2013; @sethi2012b; @sethi2014; @cline2017], but our
findings within strategies, with respect to individual year-to-year behavior,
provide new insights. Here, specializing tended to be associated with increased
revenue. This could be for a number of reasons. First, specialization can
increase fishing efficiency [@smith1986]. 
Similar efficiency gains from specialization are well known in 
agricultural fields [@ikerd1990; @abdulai2000].
Second, given the
availability of valuable resources, specializing can be highly profitable. For
instance, when cocoa prices have been high, Nigerian farmers have tended to
specialize on the crop [@mustapha1999] and specializing on valuable tobacco
farming can be the optimal strategy regardless of alternative crops
[@chavez2014]. In our analyses, fishers with the opportunity to fish highly
valuable sockeye salmon benefited the most from specializing. However,
specializing can have longterm risks if market, management, biological, or
environmental conditions change. For example, U.S. farmers specialized on wheat,
corn, or soybeans were hit harder than diversified farmers in the early 1980s
when a financial crisis hit [@ikerd1990].
Third, diversifying---a lack of
specialization---can happen as a consequence of non-ideal circumstances such
as poor availability of a more valuable resource. For example, Ugandan
households relying on forestry resources for income increase their income
portfolio diversity following downward economic shocks [@debela2012].
Because specialization inherently holds risk from ``putting all one's eggs in one
basket,'' it is not suprising that a decline in the most valuable resource
would lead to a shift towards diversification.
<!-- Response to A1 -->
Conversely, a specialization may appear as a response to increased revenue. A fisher who achieves high revenue from a hotspot of a particular fish species one year may choose to stop or pause fishing thereby indirectly limiting catch diversity. For example, pink and chum salmon are the dominant species caught in purse seine fisheries in Prince William Sound, with chum salmon generally arriving 
before pink salmon. If a fisher targeting chum achieves high revenue early in 
the season, they may choose to fish less later in the year.
